Learning dashboards: a review of scientific findings and best practices

### 2023-03-17 review_learning_dashboards_paper/paper.Rmd
Update paper.Rmd

```{r table00,echo=FALSE}
library(knitr)
library(kableExtra)
options(scipen=999)
text_decr<-data.frame(Year=c(seq(2015,2019),"All years"), News=c("4,395","5,391","5,738","8,465","6,435","30,424"),
                      Words=c("823","840","923","1,352","1,401","1,114"))
 knitr::kable(text_decr, align = "llll",
               col.names = c("Year","News Articles (merged)","Average Word Count"),
               row.names = FALSE,
               #table.attr = "id=\"table1\"",
               digits = 0,
               caption = "Description of the final textual corpus"
  )
```

>>>>

```{r table00,echo=FALSE}
library(knitr)
options(scipen=999)
text_decr<-data.frame(Year=c(seq(2015,2019),"All years"), News=c("4,395","5,391","5,738","8,465","6,435","30,424"),
                      Words=c("823","840","923","1,352","1,401","1,114"))
 knitr::kable(text_decr, align = "llll",
               col.names = c("Year","News Articles (merged)","Average Word Count"),
               row.names = FALSE,
               #table.attr = "id=\"table1\"",
               digits = 0,
               caption = "Description of the final textual corpus"
  )
```
